Figures

### 2019-12-29 manuscript/figures.Rmd
create figures pipeline
fill in caption for map
add cutoffs figure

# map

>>>>

```{r maps, fig.cap = "Map of lake maximum depth in the continental United States.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_map-1.pdf")
```

```{r cutoffs, fig.cap = "Proportion max depth availability by lake area class.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/00_cutoffs-1.pdf")
```

# exploratory analyses

# hypsography classification figure (panelized by state)
